Visual Diagnostics of a Model Explainer -- Tools for the Assessment of LIME Explanations

### 2020-08-26 paper.Rnw
small rewording

All runs of LIME in this paper are executed in a forked version\footnote{https://github.com/goodekat/lime} of the development version of the R package \emph{lime} (version \Sexpr{packageVersion("lime")}) by \kge{\citet{pedersen:2020}}. The forked version is functionally indistinguishable from \kge{\citeauthor{pedersen:2020}'s} implementation but allows us to export internal values relevant for an assessment of the explainer. The diagnostic plots included in this paper are created using the R package \emph{limeaid} \citep{goode:2020}.

>>>>

All runs of LIME in this paper are executed in a forked version\footnote{https://github.com/goodekat/lime} of the R package \emph{lime} (version \Sexpr{packageVersion("lime")}) by \kge{\citet{pedersen:2020}}. The forked version is functionally indistinguishable from \kge{\citeauthor{pedersen:2020}'s} implementation but allows us to export internal values relevant for an assessment of the explainer. The diagnostic plots included in this paper are created using the R package \emph{limeaid} \citep{goode:2020}.
